Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
rename primary and secondary stage
comment on consensus clustering

\subsection{Primary stage}

@@

\subsection{Secondary stage}

The secondary stage involves a learning based process block that will weight and linearly combine the features produced by the primary stage.

@@

>>>>

\subsection{Feature extraction}

@@

\subsection{Metric learning}

The secondary stage involves a learning-based process block that will weight and linearly combine the features produced by the primary stage.

@@

\vl{The paragraph above is the most important in the whole paper, and it deserves more attention. @writing}
